Hierarchically Supervised Latent Dirichlet Allocation

### 2011-05-31 paper/abstract.tex
updated the abstract -- is it better?

We introduce hierarchically supervised latent Dirchlet allocation (HSLDA), a model for hierarchically and multiply-labeled bag-of-words data.  Out-of-sample label prediction is the primary goal of this work; however, improved dimensionality reduction is also of interest.  We define a model that uses probit regressors on a conditionally dependent label hierarchy tied to latent Dirichlet allocation (LDA).  We find that the additional signal that comes from multiple, hierarchically constrained labels substantially improves out-of-sample label prediction in comparison to supervised LDA approaches that don't utilize information derived from the structure of the label space.   We demonstrate HSLDA on large-scale data from medical document labeling and retail product categorization tasks.  We show improved label prediction performance and evidence that the learned topic model also improves as a result of using this signal.

>>>>

We introduce hierarchically supervised latent Dirchlet allocation (HSLDA), a model for hierarchically and multiply-labeled bag-of-word data.  Examples of such data include web pages and their placement in link directories, product descriptions and placement(s) in product hierarchies, and free-text clinical records and diagnosis codes assigned to them.
Out-of-sample label prediction is the primary goal of this work, but
improved lower-dimensional representations of the bag-of-words data is also of interest.  
%We define a model that uses probit regressors on a conditionally dependent label hierarchy tied to latent Dirichlet allocation (LDA).  
We find that using the signal from hierarchical labels substantially improves out-of-sample label prediction in comparison to other models that don't utilize the structure of the labels.   We demonstrate HSLDA on large-scale data from medical document labeling and retail product categorization tasks.  We show improved label prediction performance and evidence that the learned topics also improve.
